Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Added another layout for Figure 15..to have nice layout

@@

error_mnist_umap <- read_rds("data/mnist/error_mnist_umap.rds")
error_mnist_tsne <- read_rds("data/mnist/error_mnist_tsne.rds")
error_mnist_phate <- read_rds("data/mnist/error_mnist_phate.rds")
error_mnist_trimap <- read_rds("data/mnist/error_mnist_trimap.rds")
error_mnist_pacmap <- read_rds("data/mnist/error_mnist_pacmap.rds")

error_mnist <- bind_rows(error_mnist_umap, 
                        error_mnist_tsne,
                        error_mnist_phate,
                        error_mnist_trimap,
                        error_mnist_pacmap)

@@

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8',"#ff7f00", '#999999','#a65628')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

free(error_plot_mnist) + wrap_plots(nldr_mnist1, nldr_mnist2, nldr_mnist3, 
                                    nldr_mnist4, nldr_mnist5, ncol = 2)
```

>>>>

tsne_mnist2 <- read_rds("data/mnist/mnist_tsne89.rds")

nldr_mnist6 <- tsne_mnist2 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("f", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

@@

error_mnist_umap <- read_rds("data/mnist/error_mnist_umap.rds")
error_mnist_tsne <- read_rds("data/mnist/error_mnist_tsne.rds")
error_mnist_tsne2 <- read_rds("data/mnist/error_mnist_tsne2.rds")
error_mnist_phate <- read_rds("data/mnist/error_mnist_phate.rds")
error_mnist_trimap <- read_rds("data/mnist/error_mnist_trimap.rds")
error_mnist_pacmap <- read_rds("data/mnist/error_mnist_pacmap.rds")

error_mnist <- bind_rows(error_mnist_umap, 
                        error_mnist_tsne,
                        error_mnist_tsne2,
                        error_mnist_phate,
                        error_mnist_trimap,
                        error_mnist_pacmap)

@@

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8',"#ff7f00", '#999999', '#984ea3', '#a65628')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

free(error_plot_mnist) + wrap_plots(nldr_mnist1, nldr_mnist2, nldr_mnist3, 
                                    nldr_mnist4, nldr_mnist5, nldr_mnist6, ncol = 2)
```
